---
title: ""
author: ""
date: ""
output: 
  html_document:
    code_folding: hide
---

# Table of contents

<font size="4">

* [Digitized Spectra](#dig)


* [Fraction of sensors oxidized](#oxd)

    + [OxD(R)](#oxdr)
    
    + [OxD(R')](#oxdrp)
    
    + [OxD(R'')](#oxdrpp)
    
    
* [Half cell potential](#e)

    + [E(R)](#er)
    
    + [E(R')](#erp)
    
    + [E(R'')](#erpp)
    
</font>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r initalImport}
source("Spectra_source.R")

# Import data
gfp1_dat <- read.csv("rogfp1.csv", header = FALSE, stringsAsFactors = FALSE, 
                    fileEncoding="UTF-8-BOM")
gfp2_dat <- read.csv("rogfp2.csv", header = FALSE, stringsAsFactors=FALSE,
                     fileEncoding="UTF-8-BOM")

# Create GFP1
GFP1 <- SensorPoint(gfp1_dat$V1, gfp1_dat$V2, gfp1_dat$V3, gfp1_dat$V4, -288)

# Create GFP 2
GFP2 <- SensorPoint(gfp2_dat$V1, gfp2_dat$V2, gfp2_dat$V3, gfp2_dat$V4, -272)

# Create cata ROGFP1-R12
R12 <- SensorValues(Rmax = 5.207, Rmin = 0.667, delta = 0.171, lambda_1 = 410, lambda_2 = 470)
```


<a id="dig"></a>

### Digitized Spectra

```{r Spectra}
# Plot GFP 1 and 2
par(mfrow = c(1, 2), pty = 's')
plotOxRed(GFP1, main = "GFP1")
plotOxRed(GFP2, main = "GFP2")

# Plot 
par(mfrow = c(1,1), pty = 's')
plotOxRed(R12, main = "R12 predicted", type = "p")
```

<a id="oxd"></a>

<a id="oxdr"></a>

```{r R}
# Plot OxD vs R

# Together
par(mfrow = c(1,1), pty = 's')
plotROxD(GFP1, 395, 405, 475, 485, main = "GFP1", status = TRUE)
plotROxD(GFP2, 395, 405, 490, 500, main = "GFP2", col = "purple", points = TRUE);
legend("topright", title = "Sensor", inset=c(-0.35,0), xpd=TRUE, c("GFP1", "GFP2"), pch = c(19,19), col = c("black", "purple"))

```

Although the curves look similar when plotted seperately: 
```{r RContinued}

par(pty = 's', mfrow = c(1,2))
# GFP1
plotROxD(GFP1, 395, 405, 475, 485, main = "GFP1", status = TRUE)

# GFP2
plotROxD(GFP2, 395, 405, 490, 500, main = "GFP2", col = "purple")

# Theoretical Sensor with Rmax = 6, delta = 0.2
#plotROxD(SpectraValues(Rmax = 6, Rmin = 1, delta = 0.2, lambda_1 = 410, lambda_2 = 470), 410, 410, 470, 470, main = "delta = 0.2")

# Theoretical Sensor with Rmax = 6, delta = 1
#plotROxD(SpectraValues(Rmax = 6, Rmin = 1, delta = 1, lambda_1 = 410, lambda_2 = 470), 410, 410, 470, 470, main = "delta = 1.0")
```

<a id="oxdrp"></a>

With normalized R' (R' = R/Rmin):

```{r RPrime}
# Plot OxD vs R'
# Together
par(mfrow = c(1,1), pty = 's')
plotRPrimeOxD(GFP2, 395, 405, 490, 500, main = "GFP2", color = "purple", status = TRUE);
plotRPrimeOxD(GFP1, 395, 405, 475, 485, main = "GFP1", points = TRUE)
legend("topright", title = "Sensor", inset=c(-0.35,0), xpd=TRUE, c("GFP1", "GFP2"), pch = c(19,19), col = c("black", "purple"))


# Theoretical Sensor with Rmax = 6, delta = 0.2
#plotRPrimeOxD(SpectraValues(Rmax = 6, Rmin = 1, delta = 0.2, lambda_1 = 410, lambda_2 = 470), 410, 410, 470, 470, main = "delta = 0.2")

# Theoretical Sensor with Rmax = 6, delta = 1
#plotRPrimeOxD(SpectraValues(Rmax = 6, Rmin = 1, delta = 1, lambda_1 = 410, lambda_2 = 470), 410, 410, 470, 470, main = "delta = 1.0")
```

<a id="oxdrpp"></a>

With normalized R'' (R'' = R-Rmin/Rmax-Rmin):

```{r RDoublePrime}
# Together
par(mfrow = c(1,1), pty = 's')
plotRDoublePrimeOxD(GFP2, 395, 405, 490, 500, main = "GFP2", col = "purple");
plotRDoublePrimeOxD(GFP1, 395, 405, 475, 485, main = "GFP1", points = TRUE)
legend("topright", title = "Sensor", inset=c(-0.35,0), xpd=TRUE, c("GFP1", "GFP2"), pch = c(19,19), col = c("black", "purple"))
```

<a id="e"></a>
E
<a id="er"></a>
E(R)
With ratio R:
```{r RE}
# Plot E vs R

# Together
par(mfrow = c(1,1), pty = 's')
plotRE(GFP1, 395, 405, 475, 485, main = "GFP1")
plotRE(GFP2, 395, 405, 490, 500, main = "GFP2", col = "purple", points = TRUE);
legend("topright", title = "Sensor", inset=c(-0.35,0), xpd=TRUE, c("GFP1", "GFP2"), pch = c(19,19), col = c("black", "purple"))

```


Although the curves look similar when plotted seperately: 
```{r RECont}
par(pty = 's', mfrow = c(1,2))
# GFP1
plotRE(GFP1, 395, 405, 475, 485, main = "GFP1")

# GFP2
plotRE(GFP2, 395, 405, 490, 500, main = "GFP2", col = "purple")
```

<a id="erp"></a>

With R':

```{r REPrime}
# Plot OxD vs R'
# Together
par(mfrow = c(1,1), pty = 's')
plotRPrimeE(GFP2, 395, 405, 490, 500, main = "GFP2", col = "purple");
plotRPrimeE(GFP1, 395, 405, 475, 485, main = "GFP1", points = TRUE)
legend("topright", title = "Sensor", inset=c(-0.35,0), xpd=TRUE, c("GFP1", "GFP2"), pch = c(19,19), col = c("black", "purple"))
```

<a id="erpp"></a>

With normalized R'' (R'' = R-Rmin/Rmax-Rmin):

```{r REDoublePrime}
# Together
par(mfrow = c(1,1), pty = 's')
plotRDoublePrimeE(GFP2, 395, 405, 490, 500, main = "GFP2", col = "purple");
plotRDoublePrimeE(GFP1, 395, 405, 475, 485, main = "GFP1", points = TRUE)
legend("topright", title = "Sensor", inset=c(-0.35,0), xpd=TRUE, c("GFP1", "GFP2"), pch = c(19,19), col = c("black", "purple"))
```

Now let's try some errors

First, derivative of OxD with respect to R
```{r }
# Together
par(mfrow = c(1,1), pty = 's')
plotROxD(GFP1, 395, 405, 490, 500, main = "GFP2", col = "purple", equation = dOxDdR, ylab = "dOxD", ylim = c(-100,100));
plotROxD(GFP2, 395, 405, 475, 485, main = "GFP1", points = TRUE, equation = dOxDdR, ylim = c(-100,100))

legend("topright", title = "Sensor", inset=c(-0.35,0), xpd=TRUE, c("GFP1", "GFP2"), pch = c(19,19), col = c("black", "purple"))
```
