---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
require(knitr)
require(ggplot2)
require(ggsci)
require(gridExtra)
```

```{r ggplot setup}
theme_Publication <- function(base_size=14, base_family="helvetica") {
      library(grid)
      library(ggthemes)
      (theme_foundation(base_size=base_size, base_family=base_family)
       + theme(plot.title = element_text(face = "bold",
                                         size = rel(1.2), hjust = 0.5),
               text = element_text(),
               panel.background = element_rect(colour = NA),
               plot.background = element_rect(colour = NA),
               panel.border = element_rect(colour = NA),
               axis.title = element_text(face = "bold",size = rel(1)),
               axis.title.y = element_text(angle=90,vjust =2),
               axis.title.x = element_text(vjust = -0.2),
               axis.text = element_text(), 
               axis.line = element_line(colour="black"),
               axis.ticks = element_line(),
               panel.grid.major = element_line(colour="#f0f0f0"),
               panel.grid.minor = element_blank(),
               legend.key = element_rect(colour = NA),
               legend.position = "bottom",
               legend.direction = "horizontal",
               legend.key.size= unit(0.2, "cm"),
               legend.spacing = unit(0, "cm"),
               legend.title = element_text(face="italic"),
               plot.margin=unit(c(10,5,5,5),"mm"),
               strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
               strip.text = element_text(face="bold")
          ))
      
}

# Setup ggplot
ggplot <- function(...) ggplot2::ggplot(...) + 
    scale_color_npg() +
    theme_Publication()
```

Import the unaltered medial axis data.

```{r Import_main_medialAxis_data}
Medial_R <- read.csv("Medial_lambda3.9.csv", header = FALSE)
colnames(Medial_R) <- 1:64
Medial_R <- stack(Medial_R)

Medial_Res <- read.csv("Medial_lambda3.9_residuals.csv", header = FALSE)
colnames(Medial_Res) <- 1:64
Medial_Res <- stack(Medial_Res)

Medial <- cbind(Medial_R, Medial_Res)

# Check that individuals match up
all(Medial$ind[1] == Medial$ind[2])

# Drop one individual row and relabel
Medial <- Medial[c(1,3,4)]
colnames(Medial) <- c("R", "residual", "individual")

# Add metadata
length <- length(Medial$individual)
Medial$type <- rep("R", length)
Medial$lambda <- rep(3.9, length)
Medial$experiment <- rep("tbuooh", length)
Medial$location <- rep("medial_axis", length)

kable(head(Medial))
```

Import the inverted medial axis data.

```{r Import_inverse_medialAxis_data}
Medial_Rinv <- read.csv("Medial_lambda3.9_inverse.csv", header = FALSE)
colnames(Medial_Rinv) <- 1:64
Medial_Rinv <- stack(Medial_Rinv)

Medial_Resinv <- read.csv("Medial_lambda3.9_inverse_residuals.csv", header = FALSE)
colnames(Medial_Resinv) <- 1:64
Medial_Resinv <- stack(Medial_Resinv)

Medialinv <- cbind(Medial_Rinv, Medial_Resinv)

# Check that individuals match up
all(Medialinv$ind[1] == Medialinv$ind[2])

# Drop one individual row and relabel
Medialinv <- Medialinv[c(1,3,4)]
colnames(Medialinv) <- c("R", "residual", "individual")

# Add metadata
length <- length(Medialinv$individual)
Medialinv$type <- rep("1/R", length)
Medialinv$lambda <- rep(3.9, length)
Medialinv$experiment <- rep("tbuooh", length)
Medialinv$location <- rep("medial_axis", length)

kable(head(Medialinv))
```

Combine the data into one dataframe

```{r, fig.width = 10, fig.height = 10}
Medial_all <- rbind(Medial, Medialinv)

reg <- ggplot(Medial_all, aes(R, residual, col = type)) +
  geom_point(shape = 1) +
  scale_x_continuous(limits = c(0, 6)) +
  theme(aspect.ratio=1)

abs <- ggplot(Medial_all, aes(R, abs(residual), col = type)) +
  geom_point(shape = 1) +
  scale_x_continuous(limits = c(0, 6)) +
  theme(aspect.ratio=1)

grid.arrange(reg, abs, ncol = 2)
```

Import pm3 data from the same experiment, unaltered.

```{r Import_main_pm3_data}
pm3_R <- read.csv("pm3_lambda3.9.csv", header = FALSE)
colnames(pm3_R) <- 1:64
pm3_R <- stack(pm3_R)

pm3_Res <- read.csv("pm3_lambda3.9_residuals.csv", header = FALSE)
colnames(pm3_Res) <- 1:64
pm3_Res <- stack(pm3_Res)

pm3 <- cbind(pm3_R, pm3_Res)

# Check that individuals match up
all(pm3$ind[1] == pm3$ind[2])

# Drop one individual row and relabel
pm3 <- pm3[c(1,3,4)]
colnames(pm3) <- c("R", "residual", "individual")

# Add metadata
length <- length(pm3$individual)
pm3$type <- rep("R", length)
pm3$lambda <- rep(3.9, length)
pm3$experiment <- rep("tbuooh", length)
pm3$location <- rep("pm3", length)

kable(head(pm3))
```

Import pm3 data from the same experiment, inverse.

```{r Import_inverse_pm3_data}
pm3_Rinv <- read.csv("pm3_lambda3.9_inverse.csv", header = FALSE)
colnames(pm3_Rinv) <- 1:64
pm3_Rinv <- stack(pm3_Rinv)

pm3_Resinv <- read.csv("pm3_lambda3.9_inverse_residuals.csv", header = FALSE)
colnames(pm3_Resinv) <- 1:64
pm3_Resinv <- stack(pm3_Resinv)

pm3inv <- cbind(pm3_Rinv, pm3_Resinv)

# Check that individuals match up
all(pm3inv$ind[1] == pm3inv$ind[2])

# Drop one individual row and relabel
pm3inv <- pm3inv[c(1,3,4)]
colnames(pm3inv) <- c("R", "residual", "individual")

# Add metadata
length <- length(pm3inv$individual)
pm3inv$type <- rep("1/R", length)
pm3inv$lambda <- rep(3.9, length)
pm3inv$experiment <- rep("tbuooh", length)
pm3inv$location <- rep("pm3", length)

kable(head(pm3inv))
```

Put the pm3 data into one dataframe.

```{r, fig.width = 10, fig.height = 10}
pm3_all <- rbind(pm3, pm3inv)

reg <- ggplot(pm3_all, aes(R, residual, col = type)) +
  geom_point(shape = 1) +
  scale_x_continuous(limits = c(0, 6)) +
  theme(aspect.ratio=1)

abs <- ggplot(pm3_all, aes(R, abs(residual), col = type)) +
  geom_point(shape = 1) +
  scale_x_continuous(limits = c(0, 6)) +
  theme(aspect.ratio=1)

grid.arrange(reg, abs, ncol = 2)
```

Put the medial axis and pm3 data into one dataframe.

```{r, fig.width = 10, fig.height = 10}
all_errors <- rbind(Medial_all, pm3_all)

reg <- ggplot(all_errors, aes(R, residual, col = interaction(type, location, sep = ":", lex.order=FALSE))) +
  geom_point(shape = 1) +
  labs(color="Type-Location") +
  scale_x_continuous(limits = c(0, 6)) +
  theme(aspect.ratio=1)
  
abs <- ggplot(all_errors, aes(R, abs(residual), col = interaction(type, location, sep = ":", lex.order=FALSE))) +
  geom_point(shape = 1) +
  labs(color="Type:Location") +
  scale_x_continuous(limits = c(0, 6)) +
  theme(aspect.ratio=1)
  
grid.arrange(reg, abs, ncol = 2)
```


Import pm3 data from the diamide recovery experiment, unaltered.

```{r Import_main_pm3_DA_data}
pm3_DA_R <- read.csv("pm3_lambda1_DArec.csv", header = FALSE)
colnames(pm3_DA_R) <- 1:10
pm3_DA_R <- stack(pm3_DA_R)

pm3_DA_Res <- read.csv("pm3_lambda1_DArec_residuals.csv", header = FALSE)
colnames(pm3_DA_Res) <- 1:10
pm3_DARes <- stack(pm3_DA_Res)

pm3_DA <- cbind(pm3_DA_R, pm3_DA_Res)

# Check that individuals match up
all(pm3_DA$ind[1] == pm3_DA$ind[2])

# Drop one individual row and relabel
pm3_DA <- pm3_DA[c(1,3,4)]
colnames(pm3_DA) <- c("R", "residual", "individual")

# Add metadata
length <- length(pm3_DA$individual)
pm3_DA$type <- rep("R", length)
pm3_DA$lambda <- rep(1.0, length)
pm3_DA$experiment <- rep("diamide_recovery", length)
pm3_DA$location <- rep("pm3", length)

kable(head(pm3_DA))
```

Import pm3 data from the diamide recovery experiment, inverse.

```{r Import_main_pm3_DA_inv_data}
pm3_DA_Rinv <- read.csv("pm3_lambda1_DArec_inverse.csv", header = FALSE)
colnames(pm3_DA_Rinv) <- 1:10
pm3_DA_Rinv <- stack(pm3_DA_Rinv)

pm3_DA_Resinv <- read.csv("pm3_lambda1_DArec_inverse_residuals.csv", header = FALSE)
colnames(pm3_DA_Resinv) <- 1:10
pm3_DAResinv <- stack(pm3_DA_Resinv)

pm3_DAinv <- cbind(pm3_DA_Rinv, pm3_DA_Resinv)

# Check that individuals match up
all(pm3_DAinv$ind[1] == pm3_DAinv$ind[2])

# Drop one individual row and relabel
pm3_DAinv <- pm3_DAinv[c(1,3,4)]
colnames(pm3_DAinv) <- c("R", "residual", "individual")

# Add metadata
length <- length(pm3_DAinv$individual)
pm3_DAinv$type <- rep("1/R", length)
pm3_DAinv$lambda <- rep(1.0, length)
pm3_DAinv$experiment <- rep("diamide_recovery", length)
pm3_DAinv$location <- rep("pm3", length)

kable(head(pm3_DAinv))
```

Put the pm3 diamide recovery data into one dataframe.

```{r, fig.width = 10, fig.height = 10}
pm3_DA_all <- rbind(pm3_DA, pm3_DAinv)

reg <- ggplot(pm3_DA_all, aes(R, residual, col = type)) +
  geom_point(shape = 1) +
  scale_x_continuous(limits = c(0, 6)) +
  theme(aspect.ratio=1)

abs <- ggplot(pm3_DA_all, aes(R, abs(residual), col = type)) +
  geom_point(shape = 1) +
  scale_x_continuous(limits = c(0, 6)) +
  theme(aspect.ratio=1)

grid.arrange(reg, abs, ncol = 2)
```

Add this experiment to the growing big dataframe

```{r, fig.width = 10, fig.height = 10}
all_errors <- rbind(all_errors, pm3_DA_all)

reg <- ggplot(all_errors, aes(R, residual, col = interaction(type, location, experiment, sep = ":", lex.order=FALSE))) +
  geom_point(shape = 1) +
  labs(color="Type:Location:Experiment") +
  scale_x_continuous(limits = c(0, 6)) +
  theme(aspect.ratio=1)
  
abs <- ggplot(all_errors, aes(R, abs(residual), col = interaction(type, location, experiment, sep = ":", lex.order=FALSE))) +
  geom_point(shape = 1) +
  labs(color="Type:Location:Experiment") +
  scale_x_continuous(limits = c(0, 6)) +
  theme(aspect.ratio=1)
  
grid.arrange(reg, abs, ncol = 2)

# For presentation ------------------------------------------

## Note: Keep an eye on this figure. To show relative error is independent of R
ggplot(all_errors, aes(log(R), abs(residual), sep = ":", lex.order=FALSE)) +
  geom_point(shape = 1, size = 0.05) +
  scale_x_continuous(limits = c(-2, 2)) +
    ylab("|Error in R|") +
  theme(aspect.ratio=1) +
    geom_smooth(method="lowess", se = FALSE) +
    theme(aspect.ratio=1) +
    theme(text = element_text(size=20))

topRes <- quantile(all_errors$residual/all_errors$R, 0.975)[[1]]
botRes <- quantile(all_errors$residual/all_errors$R, 0.025)[[1]]

ggplot(all_errors, aes(x = residual/R)) +
    stat_ecdf(geom="step", size = 1.5) +
    xlab("(Error in R)/R") +
    ylab("Cumulative probability") +
    geom_vline(aes(xintercept = topRes)) +
    geom_text(aes(x = topRes, y = 0.95,
                  label = "97.5%: 0.028"), angle = 0, hjust = -0.1, size = 6) +
    geom_vline(aes(xintercept = botRes))  +
    geom_text(aes(x = botRes, y = 0.05,
                  label = "2.5%: -0.028"), angle = 0, hjust = 1.1, size = 6) +
        theme(aspect.ratio=1) +
    theme(text = element_text(size=20))


```

```{r confidence}
#library(boot) 

hist(all_errors$residual, main = "All Residuals")
quantile(all_errors$residual/all_errors$R, c(.025, .975))
hist(Medial_all$residual, main = "Residuals from Medial Axis tubooh")
quantile(Medial_all$residual/Medial_all$R, c(.025, .975))
hist(pm3_all$residual, main = "Residuals from pm3 tubooh")
quantile(pm3_all$residual/pm3_all$R, c(.025, .975))
hist(pm3_DA_all$residual, main = "Residuals from pm3 diamide recovery")
quantile(pm3_DA_all$residual/pm3_DA_all$R, c(.025, .975))


# function to obtain the mean
Bmean <- function(data, indices) {
  d <- data[indices] # allows boot to select sample 
    return(mean(d))
} 


# bootstrapping with 1000 replications 
# results <- boot(data=all_errors$residual/all_errors$R, statistic=Bmean, R=1000)
# results_medial <- boot(data = Medial_all$residual/Medial_all$R, statistic=Bmean, R=1000)
# results_pm <- boot(data = pm3_all$residual/pm3_all$R, statistic=Bmean, R=1000)
# results_pm_DA <- boot(data = pm3_DA_all$residual/pm3_DA_all$R, statistic=Bmean, R=1000)
# 
# # view results
# #results 
# #plot(results)
# 
# # get 95% confidence interval 
# boot.ci(results, type=c("norm", "basic"))
# boot.ci(results_medial, type=c("norm", "basic"))
# boot.ci(results_pm, type=c("norm", "basic"))
# boot.ci(results_pm_DA, type=c("norm", "basic"))
```

```{r}
write.csv(all_errors, "error_errors.csv")

```