---
title: "Multiple Spectra Curves pHRed"
output: 
  html_document:
    code_folding: hide
      
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(sensorOverlord)
library(ggplot2)
library(tidyverse)
source("diverging_map.R")
```

```{r}
fix_spectra <- function(curve_1, pmax_1, curve_2, pmax_2) {
    new_maximum <- c()
    new_minimum <- c()

interleaved_intensities <- c(rbind(curve_1, curve_2))

for ( index in seq(1,length(interleaved_intensities),2) ) {
    b <- interleaved_intensities[index:(index+1)]
    a <- matrix(c(pmax_1, 1-pmax_1, pmax_2, 1-pmax_2), nrow = 2)
    answer <- solve(a, b)
    
    new_maximum <- c(new_maximum, answer[1])
    new_minimum <- c(new_minimum, answer[2])
    
}

return(data.frame(new_maximum = new_maximum, new_minimum = new_minimum))
       
}
```

```{r}
# Download the data
phred_data <- read.csv("../../Additional_Sensors/Analysis/PHRed/Spectra_phred_multiple.csv", header = TRUE)

# Gather the data into a tidy format
phred_data_tidy <-
gather(phred_data, pH, intensity, 
       colnames(phred_data)[grepl("X", colnames(phred_data))]) 

lambda <- gather(phred_data, value, lambda,
      colnames(phred_data)[grepl("Lambda", colnames(phred_data))])

phred_data_tidy$lambda <- lambda$lambda


phred_data_tidy$pH <- modify(phred_data_tidy$pH, 
     .f = function(x){str_replace(str_replace(x,"Lambda_", ""),"X","")})

phred_data_tidy <- drop_na(phred_data_tidy)

drops <- colnames(phred_data)[grepl("Lambda_", colnames(phred_data))]
phred_data_tidy <- phred_data_tidy[ , !(names(phred_data_tidy) %in% drops)]
```

```{r}
# Get colors
map <- diverging.colormap(seq(0,1, by = 1/7), RGB(0.230, 0.299, 0.754), 
                   RGB(0.58, 0.016, 0.150))
colors <- c()
for (i in 1:8) {
  colors <- c(colors, rgb(map[i,1], map[i,2], map[i,3], maxColorValue = 1))
}

# Graph all the phred data
ggplot(data = phred_data_tidy, aes(x = lambda, y = intensity, col = pH)) +
    geom_line(stat = "smooth", method = "auto") +
    xlab(expression(lambda (nm)))  +
    ylab("Fluorescent emission (relative)") +
    theme(aspect.ratio=1) +
    scale_color_manual(values = colors)
```

Assume a pKa of 7.8. Now we can calculate limiting curves:

For any curve, $Fraction_{Deprotenated} = \frac{10^{pH-pKa}}{1+10^{pH-pKa}}$

```{r}
frDeprot <- function(pH, pKa) {
  return((10^(pH-pKa)) / (1 + 10^{pH - pKa}))
}

new_curves <- c()

### 9 and 5.5
spectra_5.5_9.0 <- spectraMatrixFromValues(
  lambdas_minimum = phred_data$Lambda_9.0[!is.na(phred_data$Lambda_9.0)],
  values_minimum = phred_data$X9,
  lambdas_maximum = phred_data$Lambda_5.5[!is.na(phred_data$Lambda_5.5)],
  values_maximum = phred_data$X5.5)
                                            
limit_5.5_9.0 <- fix_spectra(curve_1 = spectra_5.5_9.0@values_maximum,
                                     pmax_1 = frDeprot(5.5, 7.8), 
                                     spectra_5.5_9.0@values_minimum, 
                                     pmax_2 = frDeprot(9.0, 7.8))

plottable <- data.frame(pH = "5.5_9.0_min", 
                        lambda = spectra_5.5_9.0@lambdas,
                        intensity = limit_5.5_9.0$new_minimum)
plottable <- rbind(plottable,
                   data.frame(pH = "5.5_9.0_max", 
                    lambda = spectra_5.5_9.0@lambdas,
                    intensity = limit_5.5_9.0$new_maximum))
### 6 and 8.5
spectra_6.0_8.5 <- spectraMatrixFromValues(
  lambdas_minimum = phred_data$Lambda_8.5[!is.na(phred_data$Lambda_8.5)],
  values_minimum = phred_data$X8.5,
  lambdas_maximum = phred_data$Lambda_6.0[!is.na(phred_data$Lambda_6.0)],
  values_maximum = phred_data$X6.0)
                                            
limit_6.0_8.5 <- fix_spectra(curve_1 = spectra_6.0_8.5@values_maximum,
                                     pmax_1 = frDeprot(6.0, 7.8), 
                                     spectra_6.0_8.5@values_minimum, 
                                     pmax_2 = frDeprot(8.5, 7.8))

plottable <- rbind(plottable,
                   data.frame(pH = "6.0_8.5_min", 
                   lambda = spectra_6.0_8.5@lambdas,
                   intensity = limit_6.0_8.5$new_minimum))
plottable <- rbind(plottable,
                   data.frame(pH = "6.0_8.5_max", 
                    lambda = spectra_6.0_8.5@lambdas,
                    intensity = limit_6.0_8.5$new_maximum))
### 6.5 and 8
spectra_6.5_8.0 <- spectraMatrixFromValues(
  lambdas_minimum = phred_data$Lambda_8.0[!is.na(phred_data$Lambda_8.0)],
  values_minimum = phred_data$X8.0,
  lambdas_maximum = phred_data$Lambda_6.5[!is.na(phred_data$Lambda_6.5)],
  values_maximum = phred_data$X6.5)
                                            
limit_6.5_8.0 <- fix_spectra(curve_1 = spectra_6.5_8.0@values_maximum,
                                     pmax_1 = frDeprot(6.5, 7.8), 
                                     spectra_6.5_8.0@values_minimum, 
                                     pmax_2 = frDeprot(8.0, 7.8))

plottable <- rbind(plottable,
                   data.frame(pH = "6.5_8.0_min", 
                   lambda = spectra_6.5_8.0@lambdas,
                   intensity = limit_6.5_8.0$new_minimum))
plottable <- rbind(plottable,
                   data.frame(pH = "6.5_8.0_max", 
                    lambda = spectra_6.5_8.0@lambdas,
                    intensity = limit_6.5_8.0$new_maximum))

### 7.0 and 7.5
# spectra_7.0_7.5 <- spectraMatrixFromValues(
#   lambdas_minimum = phred_data$Lambda_7.5[!is.na(phred_data$Lambda_7.5)],
#   values_minimum = phred_data$X7.5,
#   lambdas_maximum = phred_data$Lambda_7.0[!is.na(phred_data$Lambda_7.0)],
#   values_maximum = phred_data$X7.0)
#                                             
# limit_7.0_7.5 <- fix_spectra(curve_1 = spectra_7.0_7.5@values_maximum,
#                                      pmax_1 = frDeprot(7.0, 7.8), 
#                                      spectra_7.0_7.5@values_minimum, 
#                                      pmax_2 = frDeprot(7.5, 7.8))
# 
# plottable <- rbind(plottable,
#                    data.frame(pH = "7.0_7.5_min", 
#                    lambda = spectra_7.0_7.5@lambdas,
#                    intensity = limit_7.0_7.5$new_minimum))
# plottable <- rbind(plottable,
#                    data.frame(pH = "7.0_7.5_max", 
#                     lambda = spectra_7.0_7.5@lambdas,
#                     intensity = limit_7.0_7.5$new_maximum))

```

Here are the predicted limiting curves (for example, 5.5_9.0_min is the Rmin limiting
curve predicted by the 5.5 and 9.0 non-limiting curves)

```{r}
colors <- colors[c(1,8,2,7,3,6,4,5)]
# Graph all the phred data
ggplot(data = plottable, aes(x = lambda, y = intensity, col = pH)) +
    geom_line(stat = "smooth", method = "auto") +
    xlab(expression(lambda (nm)))  +
    ylab("Fluorescent emission (relative)") +
    theme(aspect.ratio=1) +
    scale_color_manual(values = colors)
```


Here are those limiting curve predictions alongside the real curves.

I did compute the 7.0_7.5 curve, but it was too extreme--it had emission up to 2.0.

```{r}
colors <- c(rep("black", 8),colors)

# Swap plottable rows
plottable <- plottable[c("pH", "intensity", "lambda")]

# combine phred and plottable
plottable_combined <- rbind(phred_data_tidy, plottable)

# Graph all the phred data
plottable_combined$pH <- factor(plottable_combined$pH, 
                                levels = unique(plottable_combined$pH))

ggplot(data = plottable_combined, aes(x = lambda, y = intensity, col = pH)) +
    geom_line(stat = "smooth", method = "auto") +
    xlab(expression(lambda (nm)))  +
    ylab("Fluorescent emission (relative)") +
    theme(aspect.ratio=1) +
    scale_color_manual(values = colors)
```


Finding a pKa from the graph is going to be tricky and I'll
need to think about it more.

##
```{r}
# plot(x = seq(5.5,9, by = 0.5), y = c(phred_data$X5.5[1], 
#                                      phred_data$X6.0[1],
#                                      phred_data$X6.5[1], 
#                                      phred_data$X7.0[1], 
#                                      phred_data$X7.5[1], 
#                                      phred_data$X8.0[1], 
#                                      phred_data$X8.5[1],
#                                      phred_data$X9[1]), type = 'l', ylim = c(0,1))
# 
# for (i in 2:50) {
#   points(x = seq(5.5,9, by = 0.5), y = c(phred_data$X5.5[i], 
#                                      phred_data$X6.0[i],
#                                      phred_data$X6.5[i], 
#                                      phred_data$X7.0[i], 
#                                      phred_data$X7.5[i], 
#                                      phred_data$X8.0[i], 
#                                      phred_data$X8.5[i],
#                                      phred_data$X9[i]), type = 'l')
# }

```