---
title: "A tale of two errors"
author: ""
date: "October 31, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### The origin of the error

There is an error in the recorded measurements at both of your sensor's excitation wavelengths, $\lambda_1$ and $\lambda_2$. 

\

$I_{\lambda_1}$ is off by some factor: $I_{\lambda_1, actual} = I_{\lambda_1} + a$

$I_{\lambda_2}$ is off by some factor: $I_{\lambda_2, actual} = I_{\lambda_2} + b$

\

Let's say your emission of interest, $R$, is measured as $\frac{I_{\lambda_1}}{I_{\lambda_2}}$. And all of your results assume that $R = \frac{I_{\lambda_1}}{I_{\lambda_2}}$, when in fact $R_{actual} = \frac{I_{\lambda_1} + a}{I_{\lambda_2} + b}$. 

\

The actual amount of error in $R$ will depend on $I_{\lambda_1}$ and $I{\lambda_2}$ ($\Delta R = \frac{I_{\lambda_1} + a}{I{\lambda_2} + b} - \frac{I{\lambda_1}}{I_{\lambda_2}}$).But let's define a constant error $c$: $R_{actual} = c * \frac{I_{\lambda_1}}{I_{\lambda_2}}$. Perhaps an estimate of $c$ could be obtained by measuring the variation in measured ratios from a data sample. 

### The error propagating to OxD

First, let's imagine that you have an error of $c = 1.05$. How much will that change the OxD?


**TODO: Graph**

But really that error will just shift our graph to the left or right. Think about it: you're at an R of 1 but the actual R is 1.05, so the graph will just shift.

\

That will have the same effect on the graph of E, since it is also plotted with respect to R.

\

But, if $c = 1.05$, how will that effect the other values?

\

Rmin and Rmax will both be changed by $1.05$, so those effects will also just scale the graph horizontally. 

\

The relative contribution of each wavelength $\delta$ will be changed differently, since it is measured entirely in the $\lambda_2$ wavelength:

Assuming that $\lambda_2$ has a constant error regardless of the conditions, $\Delta \delta = \frac{I_{\lambda_2, ox} + a}{I_{\lambda_2, red} + a} - \frac{I_{\lambda_2, ox}}{I_{\lambda_2, red}} = \frac{a(I_{lambda_2, red} - I_{lambda_2, ox})}{I_{lambda_2, red}(I_{lambda_2,red} + a)}$. 


### Baseline errors

```{r}
R <- read.csv("R_vab_11_15_18.csv")
R_animal1 <- subset(R, R$Strains == 1)
R_animal2 <- subset(R, R$Strains == 2)
R_animal1_nomvmt <- subset(R_animal1, R_animal1$Movement == 0)
R_animal2_nomvmt <- subset(R_animal2, R_animal2$Movement == 0)
```

Let's look at all of the traces
```{r}
y <- c()
for (pos in 1:100) {
    y <- c(y, R_animal1[1, pos])
}

plot(y, ylim = c(0.5,1.5), type = "l")

for (animal in (1:100)) {
    y <- c()
    for (pos in 1:100) {
        y <- c(y, R_animal1[animal, pos])
    }
    points(y, type = "l")
}

```


```{r}
dim(R_animal1_nomvmt)[1]
dim(R_animal2_nomvmt)[1]
```

We have 35 of one animal that didn't have any movement, and 22 of another animal that didn't have any movement.

What is the standard error at each position?

```{r}
# Define standard error
se <- function(x) sqrt(var(x)/length(x))

# Initalize vector
errors_animal1 <- c()
errors_animal2 <- c()

# Loop through positions, add standard error to vector
for (i in (1:100)) {
    errors_animal1 <- c(errors_animal1, se(R_animal1_nomvmt[i]))
    errors_animal2 <- c(errors_animal2, se(R_animal2_nomvmt[i]))
}

plot(errors_animal1, col = "black", ylim = c(0, 0.2), pch = 20)
points(errors_animal2, col = "red", pch = 20)
```

What if we do the same thing for all of the animals?

```{r}
# Initalize vector
errors_animal1_all <- c()
errors_animal2_all <- c()

# Loop through positions, add standard error to vector
for (i in (1:100)) {
    errors_animal1_all <- c(errors_animal1_all, se(R_animal1[i]))
    errors_animal2_all <- c(errors_animal2_all, se(R_animal2[i]))
}

plot(errors_animal1_all, col = "black", ylim = c(0, 0.2), pch = 20)
points(errors_animal2_all, col = "red", pch = 20)
```

Let's take a more extreme value--say, the range. How does that compare?


```{r}
# Initalize vector
range_animal1 <- c()
range_animal2 <- c()

# Loop through positions, add standard error to vector
for (i in (1:100)) {
    range_animal1 <- c(range_animal1, range(R_animal1_nomvmt[i])[2])
    range_animal2 <- c(range_animal2, range(R_animal2_nomvmt[i])[2])
}

plot(range_animal1, col = "black", ylim = c(0, 3), pch = 20)
points(range_animal2, col = "red", pch = 20)
```

```{r}
# Initalize vector
range_animal1_all <- c()
range_animal2_all <- c()

# Loop through positions, add standard error to vector
for (i in (1:100)) {
    range_animal1_all <- c(range_animal1_all, range(R_animal1[i])[2])
    range_animal2_all <- c(range_animal2_all, range(R_animal2[i])[2])
}

plot(range_animal1_all, col = "black", ylim = c(0, 3), pch = 20)
points(range_animal2_all, col = "red", pch = 20)
```
